---
title: "Autism-Part1"
author: "chenhy"
date: "2020/6/25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library packages, message=FALSE, warning=FALSE, include=FALSE}
library(NetBID2)
library(tidyverse)
library(stringr)
library(VennDiagram)
library(grid)
library(futile.logger)
```
# Find drivers in autism by using NetBID2
## Get significantly up/down regulated genes and drivers
GSE_info:

```{r get_gse_info, echo=FALSE}
gse_info <- openxlsx::read.xlsx("/cluster/home/chenhy/project/neuron_drivers_landscape/data/Autism_info.xlsx",1)
gse_info_select <- gse_info[which(gse_info$GSE_code %in% c("GSE27919067","GSE28521","GSE64018")),c("GSE_code","GPL","Study.type","Case","Control","Age","Race","Tissue")]
knitr::kable(gse_info_select,format = "html",row.names = F) %>% kable_styling(full_width = T)
```

## Data pre-processing
The path of pre-processing cede is /cluster/home/chenhy/project/neuron_drivers_landscape/src  
The path of QC plot is /cluster/home/chenhy/project/neuron_drivers_landscape/data/{GSE_name}/QC
```{r pre-processing, echo=TRUE, message=FALSE, warning=FALSE}
###### Step 1: Load in gene expression datasets for network construction (exp-load)
#### Download expression dataset from GEO, need to provide GSE ID and GPL ID
### Remove duplicated data & # ID conversion using transfer_tab

###### Step 2: Normalization for the expression dataset (exp-QC)
#### Firstly, view missing values for rows and columns
#### Secondly, the log2 transformation.
#### Thirdly, the quantile normalization across samples.
#### Fourthly, filter out genes with very low expression values (bottom 5%) in most samples (more than 90%).

###### Step 3: Cluster analysis using Kmean and plot result using PCA biplot (pca+kmeans in 2D)
##### Finding confounding factors and remove batch effect

###### Step 4: Get differential expression (DE) / differential activity (DA) for drivers (act-DA) 
```
Get regulated drivers:

```{r get_drivers, message=FALSE, warning=FALSE}
## input GSE data
gse_list <- list()
for (i in 1:nrow(gse_info_select)) {
  project_main_dir <- "/cluster/home/chenhy/project/neuron_drivers_landscape/data/"
  project_name <- sprintf('Autism_%s_%s',gse_info_select[i,"GSE_code"],gse_info_select[i,"GPL"])
  analysis.par <- list()
  analysis.par$out.dir.DATA <- file.path(project_main_dir,project_name,"DATA/")
  NetBID.loadRData(analysis.par=analysis.par,step='ms-tab')
  gse_list[[gse_info_select[i,"GSE_code"]]] <-  analysis.par
  rm(analysis.par)
}
```

### PCA for GSE27919067 cal.eset
Data processing details: 数据已矫正批次效应
```{r pca_GSE27919067_cal.eset, echo=FALSE, message=FALSE, warning=FALSE,fig.width=9}
analysis.par <- gse_list[["GSE27919067"]]
phe <- pData(analysis.par$cal.eset)
mat <- exprs(analysis.par$cal.eset)
intgroup <- c("ASD.CTL")
draw.emb.kmeans(mat=mat,all_k = NULL,obs_label=get_obs_label(phe,intgroup),verbose=FALSE)
```

### PCA for GSE27919067 merge.ac.eset
Data processing details: 数据已矫正批次效应
```{r pca_GSE27919067_merge.ac.eset, echo=FALSE, message=FALSE, warning=FALSE,fig.width=9}
analysis.par <- gse_list[["GSE27919067"]]
phe <- pData(analysis.par$merge.ac.eset)
mat <- exprs(analysis.par$merge.ac.eset)
intgroup <- c("ASD.CTL")
draw.emb.kmeans(mat=mat,all_k = NULL,obs_label=get_obs_label(phe,intgroup),verbose=FALSE)
```

### PCA for GSE28521 cal.eset
Data processing details: 数据没有协变量，未矫正批次效应
```{r pca_GSE28521_cal.eset, echo=FALSE, message=FALSE, warning=FALSE,fig.width=9}
analysis.par <- gse_list[["GSE28521"]]
phe <- pData(analysis.par$cal.eset)
mat <- exprs(analysis.par$cal.eset)
intgroup <- c("disease status")
draw.emb.kmeans(mat=mat,all_k = NULL,obs_label=get_obs_label(phe,intgroup),verbose=FALSE)
```

### PCA for GSE28521 merge.ac.eset
Data processing details: 数据没有协变量，未矫正批次效应
```{r pca_GSE28521_merge.ac.eset, echo=FALSE, message=FALSE, warning=FALSE,fig.width=9}
analysis.par <- gse_list[["GSE28521"]]
phe <- pData(analysis.par$merge.ac.eset)
mat <- exprs(analysis.par$merge.ac.eset)
intgroup <- c("disease status")
draw.emb.kmeans(mat=mat,all_k = NULL,obs_label=get_obs_label(phe,intgroup),verbose=FALSE)
```

### PCA for GSE64018 cal.eset
Data processing details: 根据原文表述数据可能已矫正批次效应
```{r pca_GSE64018_cal.eset, echo=F, message=FALSE, warning=FALSE,fig.width=9}
analysis.par <- gse_list[["GSE64018"]]
phe <- pData(analysis.par$cal.eset)
mat <- exprs(analysis.par$cal.eset)
intgroup <- c("diagnosis")
draw.emb.kmeans(mat=mat,all_k = NULL,obs_label=get_obs_label(phe,intgroup),verbose=FALSE)
```

### PCA for GSE64018 merge.ac.eset 
Data processing details: 根据原文表述数据可能已矫正批次效应
```{r pca_GSE64018_merge.ac.eset, echo=F, message=FALSE, warning=FALSE,fig.width=9}
analysis.par <- gse_list[["GSE64018"]]
phe <- pData(analysis.par$merge.ac.eset)
mat <- exprs(analysis.par$merge.ac.eset)
intgroup <- c("diagnosis")
draw.emb.kmeans(mat=mat,all_k = NULL,obs_label=get_obs_label(phe,intgroup),verbose=FALSE)
```


## Expression level
## Plot Venn graph
Significantly different expression genes as a proportion of all genes
```{r echo=FALSE, message=FALSE, warning=FALSE}
source("get_sig_genes.R")
sprintf("%s:%s",names(gse_list)[3],round(nrow(gse27919067_all_gene)/nrow(gse_list[["GSE27919067"]]$DE$ASD.Vs.TD),3))
sprintf("%s:%s",names(gse_list)[1],round(nrow(gse64018_all_gene)/nrow(gse_list[["GSE64018"]]$DE$ASD.Vs.TD),3))
sprintf("%s:%s",names(gse_list)[2],round(nrow(gse28521_all_gene)/nrow(gse_list[["GSE28521"]]$DE$ASD.Vs.TD),3))

```


## The overlap of all protein-conding genes in the three raw datasets

```{r venn_raw_data, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=6}
source("Venn_raw_data_protein_coding.R")
```

## The overlap of all protein-conding genes in the three processed datasets

```{r venn_remove0_data, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=6}
source("Venn_final_data_protein_coding.R")
```

## The overlap of differential genes in the three datasets is shown below  

Up genes
```{r venn_up, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=6}
source("VennDiagram_gene_up.R")
```

Down genes
```{r venn_down, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=6}
source("VennDiagram_gene_down.R")
```

## Plot pheatmap of overlaps genes of GSE27919067 and GSE28521

### The expression of up/down regulated genes in GSE27919067
```{r pheatmap_up_GSE27919067, echo=FALSE, message=FALSE, warning=FALSE}
source("pheatmap_function_DE.R") #source the function for ploting pheatmap
A <- gse27919067_all_gene$ID
B <- gse28521_all_gene$ID
C <- gse64018_all_gene$ID
intersect_gene <- Reduce(union,list(v1=intersect(A,C),
                                    v2=intersect(A,B),
                                    v3=intersect(B,C)))
GSE27919067_DE <- gse_list[["GSE27919067"]]$DE$ASD.Vs.TD %>% .[which(.$ID %in% intersect_gene),]
plot_gse_pheatmap_DE(gse = gse_list[["GSE27919067"]], gse_DE = GSE27919067_DE, status = "up/down", use_phe = c("ASD.CTL"))
```
### The expression of up/down regulated genes in GSE64018
```{r pheatmap_up_GSE64018, echo=FALSE, message=FALSE, warning=FALSE}
gse64018_DE <- gse_list[["GSE64018"]]$DE$ASD.Vs.TD %>% .[which(.$ID %in% intersect(A,C)),]
plot_gse_pheatmap_DE(gse = gse_list[["GSE64018"]], gse_DE = gse64018_DE, status = "up/down", use_phe = c("diagnosis"))
```

### The expression of up/down regulated genes in GSE28521
```{r pheatmap_up_GSE28521, echo=FALSE, message=FALSE, warning=FALSE}
gse28521_DE <- gse_list[["GSE28521"]]$DE$ASD.Vs.TD %>% .[which(.$ID %in% intersect(A,B)),]
plot_gse_pheatmap_DE(gse = gse_list[["GSE28521"]], gse_DE = gse28521_DE, status = "up/down", use_phe = c("disease status"))
```

## Intersection with public reported genes
check the intersection of up/down with public reported autism related genes in DisGenet
```{r check intersection up, echo=FALSE, message=FALSE, warning=FALSE, comment=''}
disgenet_gene <- read.table(file = "/cluster/home/chenhy/project/neuron_drivers_landscape/data/C1510586_disease_gda_summary.tsv",sep = "\t",quote = "",header = T,stringsAsFactors = F)
sfari_gene <- read.csv("/cluster/home/chenhy/project/neuron_drivers_landscape/data/SFARI-Gene_genes_05-19-2020release_06-30-2020export.csv",stringsAsFactors = F)

disgenet_gene <- disgenet_gene[which(disgenet_gene$Gene %in% intersect_gene),]
sfari_gene <- sfari_gene[which(sfari_gene$gene.symbol %in% intersect_gene),]
sprintf("Tht number of intersect gene is %s. The number of DisGenet reported gene in the overlap of DEG is %s, mean Disease-related-score in DisGenet equals %s",length(intersect_gene),nrow(disgenet_gene),round(mean(disgenet_gene$Score_gda),3))
```

```{r check intersection down, echo=FALSE, message=FALSE, warning=FALSE, comment=''}
sprintf("The number of SFari reported gene in the overlap of DEG is %s, mean Disease-related-score in SFari equals %s",nrow(sfari_gene),round(mean(sfari_gene$gene.score,na.rm=T),3))
```

## Activity level
## Plot Venn graph
Significantly different drivers as a proportion of all drivers
```{r echo=FALSE, message=FALSE, warning=FALSE}
source("get_sig_drivers.R")
sprintf("%s:%s",names(gse_list)[3],round(nrow(gse27919067_all_driver)/nrow(gse_list[[1]]$final_ms_tab),3))
sprintf("%s:%s",names(gse_list)[1],round(nrow(gse64018_all_driver)/nrow(gse_list[[2]]$final_ms_tab),3))
sprintf("%s:%s",names(gse_list)[2],round(nrow(gse28521_all_driver)/nrow(gse_list[[3]]$final_ms_tab),3))

```

## The overlap of drivers in the three datasets is shown below  

Up drivers
```{r venn_drivers_up, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=6}
source("VennDiagram_drivers_up.R")
```

Down drivers
```{r venn_drivers_down, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=6}
source("VennDiagram_drivers_down.R")
```

## Plot pheatmap of overlaps drivers of GSE27919067,GSE64018 and GSE28521

### The activity of up/down regulated drivers in GSE27919067
```{r pheatmap_GSE27919067_ac, echo=FALSE, message=FALSE, warning=FALSE}
source("pheatmap_function_DA.R")
A <- gse27919067_all_driver[which(gse27919067_all_driver$logFC.ASD.Vs.TD_DA>0),]$originalID_label
B <- gse28521_all_driver[which(gse28521_all_driver$logFC.ASD.Vs.TD_DA>0),]$originalID_label
C <- gse64018_all_driver[which(gse64018_all_driver$logFC.ASD.Vs.TD_DA>0),]$originalID_label
intersect_driver_up <- Reduce(union,list(v1=intersect(A,C),
                                      v2=intersect(A,B),
                                      v3=intersect(B,C)))
A <- gse27919067_all_driver[which(gse27919067_all_driver$logFC.ASD.Vs.TD_DA<0),]$originalID_label
B <- gse28521_all_driver[which(gse28521_all_driver$logFC.ASD.Vs.TD_DA<0),]$originalID_label
C <- gse64018_all_driver[which(gse64018_all_driver$logFC.ASD.Vs.TD_DA<0),]$originalID_label
intersect_driver_down <- Reduce(union,list(v1=intersect(A,C),
                                      v2=intersect(A,B),
                                      v3=intersect(B,C)))
intersect_driver <- c(intersect_driver_up,intersect_driver_down)
GSE27919067_DA <- gse_list[["GSE27919067"]]$final_ms_tab %>% .[which(.$originalID_label %in% intersect_driver),]
gse27919067_all_driver_up <- nrow(gse27919067_all_driver[which(gse27919067_all_driver$originalID_label %in%  intersect_driver_up & gse27919067_all_driver$logFC.ASD.Vs.TD_DA>0),])
gse27919067_all_driver_down <- nrow(gse27919067_all_driver[which(gse27919067_all_driver$originalID_label %in%  intersect_driver_down & gse27919067_all_driver$logFC.ASD.Vs.TD_DA<0),])
sprintf("The number of up regulated drivers in GSE27919067 is %s,the percentage of all differential up drivers is %s;down regulated drivers is %s,the percentage of all differential down drivers is %s",gse27919067_all_driver_up,round(gse27919067_all_driver_up/nrow(gse27919067_all_driver),2),gse27919067_all_driver_down,round(gse27919067_all_driver_down/nrow(gse27919067_all_driver),2))

plot_gse_pheatmap_DA(gse = gse_list[["GSE27919067"]], gse_DA = GSE27919067_DA, status = "up/down", use_phe = c("ASD.CTL"))
```

### The activity of up/down regulated drivers in GSE64018
```{r pheatmap_GSE64018_ac, echo=FALSE, message=FALSE, warning=FALSE}
gse64018_DA <- gse_list[["GSE64018"]]$final_ms_tab %>% .[which(.$originalID_label %in% intersect_driver),]
gse64018_all_driver_up <- nrow(gse64018_all_driver[which(gse64018_all_driver$originalID_label %in%  intersect_driver_up & gse64018_all_driver$logFC.ASD.Vs.TD_DA>0),])
gse64018_all_driver_down <- nrow(gse64018_all_driver[which(gse64018_all_driver$originalID_label %in%  intersect_driver_down & gse64018_all_driver$logFC.ASD.Vs.TD_DA<0),])
sprintf("The number of up regulated drivers in GSE64018 is %s,the percentage of all differential up drivers is %s;down regulated drivers is %s,the percentage of all differential down drivers is %s",gse64018_all_driver_up,round(gse64018_all_driver_up/nrow(gse64018_all_driver),2),gse64018_all_driver_down,round(gse64018_all_driver_down/nrow(gse64018_all_driver),2))
plot_gse_pheatmap_DA(gse = gse_list[["GSE64018"]], gse_DA = gse64018_DA, status = "up/down", use_phe = c("diagnosis"))
```

### The activity of up/down regulated drivers in GSE28521
```{r pheatmap_GSE28521_ac, echo=FALSE, message=FALSE, warning=FALSE}
gse28521_DA <- gse_list[["GSE28521"]]$final_ms_tab %>% .[which(.$originalID_label %in% intersect_driver),]
gse28521_all_driver_up <- nrow(gse28521_all_driver[which(gse28521_all_driver$originalID_label %in%  intersect_driver_up & gse28521_all_driver$logFC.ASD.Vs.TD_DA>0),])
gse28521_all_driver_down <- nrow(gse28521_all_driver[which(gse28521_all_driver$originalID_label %in%  intersect_driver_down & gse28521_all_driver$logFC.ASD.Vs.TD_DA<0),])
sprintf("The number of up regulated drivers in GSE28521 is %s,the percentage of all differential up drivers is %s;down regulated drivers is %s,the percentage of all differential down drivers is %s",gse28521_all_driver_up,round(gse28521_all_driver_up/nrow(gse28521_all_driver),2),gse28521_all_driver_down,round(gse28521_all_driver_down/nrow(gse28521_all_driver),2))
plot_gse_pheatmap_DA(gse = gse_list[["GSE28521"]], gse_DA = gse28521_DA, status = "up/down", use_phe = c("disease status"))
```




